A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-10 4_method.tex
lil

\subsubsection{Background}
The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \todo{[citation needed]}
See \cref{MAT_explanation}.

@@

The medial axis along with the feature radius combine into a complete feature decsriptor, called the medial axis transform (MAT).
The MAT can unambiguously recreate the exact input shape. \todo{[citation needed]}

>>>>

\subsubsection{Background}
One of the most commonly used skeletonizations of a shape is the medial axis.
The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \todo{[citation needed]}
See \cref{MAT_explanation}.

@@

The medial axis along with the feature radius combine into a complete feature decsriptor, called the medial axis transform (MAT).
The MAT can unambiguously recreate the input shape exactly. \todo{[citation needed]}
